Parametrization of Invertible Resnets up to Homology Equivalence for Abelian Lie Groups

### 2020-04-02 llncs2e/paper77.tex
data

An analogous argument shows, that for some face of a singular simplex $\tilde{\sigma}$, restricted to $U \cap \partial_j \Delta^k$, the inductive step can be completed as follows:
\begin{align}
&\tilde{\sigma} \circ \left(v_1,\cdots,v_{j-1},0,v_{j+1},\cdots, v_n\right) = \\
= \; &\tilde{\sigma}_0 \circ \left(v_1, \cdots, x_{j-1}, 0, v_{j+1}, \cdots, v_n\right) - \\
&- \tilde{\sigma}_0 \circ \left(v_1, \cdots, v_{j-1}, 0, v_{j+1}, \cdots, v_n\right) + \\
&+ \tilde{\sigma}_j \circ \left(v_1, \cdots, v_{j-1}, 0, v_{j+1}, \cdots, v_n\right) = \\
= \; &\sigma \circ \left(v_1, \cdots, v_{i-1}, 0, v_{i+1}, \cdots, v_n\right).
\end{align}
\qed
\end{proof}
Prop. \ref{smoothextension} proofs the lemma, as every $v_i \in \partial \Delta^k$ has a smooth extension for arbitrary $k$, every element of any simplex has a smooth extension.
\qed
\end{proof}

@@

\begin{lemma}
\label{smoothhomtop}
For every $k$-simplex $\sigma: \Delta^k \rightarrow M$ from the standard $k$-simplex of $\mathbb{R}^n$ to $M$, there exists a continous map $h_\sigma: \Delta^k \times I \rightarrow M$, beeing a homotopy, satisfying the following conditions:
\begin{itemize}
	\item[(1)] $h_\sigma$ maps from $\sigma(v) = h_\sigma(v,0)$ to a smooth $k$-simplex $\tilde{\sigma}(v) = h_\sigma(v,1)$.
	\item[(2)] For each boundary face inclusion $s_{i,k}: \Delta^{k-1} \simeq \partial_{i} \Delta^k \hookrightarrow \Delta^{k}$, we get \\$h_{\sigma \circ s_{i,k}}(v,t)$ $=$ $h_\sigma(s_{i,k}(v),t)$ for $(v,t) \in \Delta^{k-1} \times I$.
	\item[(3)] For a smooth $k$-simplex $\sigma$, $h_\sigma$ is the constant homotopy, i.e. $h_{\sigma}(v,t) = \sigma(v)$.
\end{itemize}
\end{lemma}

@@

\subsubsection{Invertible $\mathcal{C}^1$-Net}
\label{appx:invarch}
The neural net used in Sect. \ref{sec:numericalexperiments} is a partially invertible architecture. It consists of a total of five hidden layers. The first layer is a dense layer, which connects the input $\mathbf{x}^{(0)} \mapsto \text{BN}\left(\sigma\left(\sum_{i=1}^{n} \textbf{W}^{(1)}_{ji}\mathbf{x}^{(0)}_{i} + \mathbf{b}^{(1)}_{i}\right)\right)$ to a subspace of $\mathbf{x}^{(0)} \in \mathbb{R}^n$. The subspace is initially $\mathbb{R}^{n-k}$ with $(n-k) \leq n$, according to Fig. \ref{architecture}. The sigmoid function is used as activation function. The weights are initialized uniformly distributed and the bias term is with zeros, respectively. The batch normalization can be expressed for a batch $k$ at the $l$-th layer as
\begin{align}
	\text{BN}(\mathbf{x}^{(l)}_{(k)})_{\gamma^{(l)}_{(k)},\beta^{(l)}_{(k)}} = \frac{\gamma}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}] + \epsilon}} \mathbf{x}^{(l)}_{(k)} + \left( \beta - \frac{\gamma \text{E}[\mathbf{x}^{(l)}_{(k)}]}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}]+\epsilon}} \right),
\end{align}
where $\gamma,\beta$ and $\epsilon$ are free parameters updated during back propagation. The very first and last dense layer is not invertible. Its purpose is a learned projection into the desired subspace of dimension $(n-k)$ for some $k$ and afterwards projecting into the original space in an encoding fashion, see Fig. \ref{architecture}.

>>>>

An analogous argument shows, that for any face of a singular simplex $\tilde{\sigma}$, restricted to $U \cap \partial_j \Delta^k$, the inductive step can be completed as follows:
\begin{align}
&\tilde{\sigma} \circ \left(v_1,\cdots,v_{j-1},0,v_{j+1},\cdots, v_n\right) = \\
= \; &\tilde{\sigma}_0 \circ \left(v_1, \cdots, x_{j-1}, 0, v_{j+1}, \cdots, v_n\right) - \\
&- \tilde{\sigma}_0 \circ \left(v_1, \cdots, v_{j-1}, 0, v_{j+1}, \cdots, v_n\right) + \\
&+ \tilde{\sigma}_j \circ \left(v_1, \cdots, v_{j-1}, 0, v_{j+1}, \cdots, v_n\right) = \\
= \; &\sigma \circ \left(v_1, \cdots, v_{i-1}, 0, v_{i+1}, \cdots, v_n\right).
\end{align}
\qed
\end{proof}
Prop. \ref{smoothextension} proofs the lemma, as every $v_i \in \partial \Delta^k$ has a smooth extension for arbitrary $k$, every element of any simplex has a smooth extension.
\qed
\end{proof}

@@

\begin{lemma}
\label{smoothhomtop}
For every $k$-simplex $\sigma: \Delta^k \rightarrow M$ from the standard $k$-simplex of $\mathbb{R}^n$ to $M$, there exists a continuous map $h_\sigma: \Delta^k \times I \rightarrow M$, beeing a homotopy, satisfying the following conditions:
\begin{itemize}
	\item[(1)] $h_\sigma$ maps from $\sigma(v) = h_\sigma(v,0)$ to a smooth $k$-simplex $\tilde{\sigma}(v) = h_\sigma(v,1)$.
	\item[(2)] For each boundary face inclusion $s_{i,k}: \Delta^{k-1} \simeq \partial_{i} \Delta^k \hookrightarrow \Delta^{k}$, we get \\$h_{\sigma \circ s_{i,k}}(v,t)$ $=$ $h_\sigma(s_{i,k}(v),t)$ for $(v,t) \in \Delta^{k-1} \times I$.
	\item[(3)] For a smooth $k$-simplex $\sigma$, $h_\sigma$ is the constant homotopy, i.e. $h_{\sigma}(v,t) = \sigma(v)$.
\end{itemize}
\end{lemma}

@@

\subsubsection{Invertible $\mathcal{C}^1$-Net}
\label{appx:invarch}
The neural net used in Sect. \ref{sec:numericalexperiments} is a partially invertible architecture. It consists of a total of five hidden layers. The first layer is a dense layer, which connects the input $\mathbf{x}^{(0)} \mapsto \text{BN}\left(\sigma\left(\sum_{i=1}^{n} \textbf{W}^{(1)}_{ji}\mathbf{x}^{(0)}_{i} + \mathbf{b}^{(1)}_{i}\right)\right)$ to a subspace of $\mathbf{x}^{(0)} \in \mathbb{R}^n$. The subspace is initially $\mathbb{R}^{n-k}$ with $(n-k) \leq n$, according to Fig. \ref{architecture}. The sigmoid function is used as activation function. The weights are initialized uniformly distributed and the bias term is with zeros, respectively. The batch normalization can be expressed for a batch $k$ at the $l$-th layer as
\begin{align}
	\text{BN}(\mathbf{x}^{(l)}_{(k)})_{\gamma^{(l)}_{(k)},\beta^{(l)}_{(k)}} = \frac{\gamma}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}] + \epsilon}} \mathbf{x}^{(l)}_{(k)} + \left( \beta - \frac{\gamma \text{E}[\mathbf{x}^{(l)}_{(k)}]}{\sqrt{\text{Var}[\mathbf{x}^{(l)}_{(k)}]+\epsilon}} \right),
\end{align}
where $\gamma,\beta$ and $\epsilon$ are parameters updated during back propagation. The very first and last dense layer is not invertible. Its purpose is a learned projection into the desired subspace of dimension $(n-k)$ for some $k$ and afterwards projecting into the original space in an encoding fashion, see Fig. \ref{architecture}.
